---
title: "Project Milestone 5"
author: "Chloe Bui & Jeffrey Smith"
date: "2024-11-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(colorspace)
library(readr)
ds=read_csv("https://raw.githubusercontent.com/jysmochi/data_502_project_stuff/refs/heads/main/train.csv?token=GHSAT0AAAAAAC2PWFVNORIY5I463VHD3HAGZZWISCA")
```


#1 Wrangle the data
```{r}
dsDummy = ds %>% 
  mutate(Gender=factor(Gender),
         Driving_License=factor(Driving_License),
         Region_Code = factor(Region_Code),
         Previously_Insured = factor(Previously_Insured),
         Vehicle_Age = factor(Vehicle_Age),
         Vehicle_Damage = factor(Vehicle_Damage),
         Policy_Sales_Channel = factor(Policy_Sales_Channel))

ds = ds %>% 
  mutate(Gender=factor(Gender),
         Driving_License=factor(Driving_License),
         Region_Code = factor(Region_Code),
         Previously_Insured = factor(Previously_Insured),
         Vehicle_Age = factor(Vehicle_Age),
         Vehicle_Damage = factor(Vehicle_Damage),
         Policy_Sales_Channel = factor(Policy_Sales_Channel),
         Response = factor(Response))

# Summarize the data to calculate the proportion of customers interested in insurance per region
region_summary <- ds %>%
  group_by(Region_Code) %>%
  summarise(
    Total_Customers = n(),
    Interested_Customers = sum(as.numeric(Response == 1)),
    Interest_Rate = round (Interested_Customers / Total_Customers * 100,1),
    total_annual_Premium = round (sum(Annual_Premium)/1000000,2))

# Order the data by Interest_Rate in descending order
region_summary_desc <- region_summary %>%
  arrange(desc(Interest_Rate))
# choose top 10
region_summary_desc_10 = region_summary_desc %>% 
  head(10)
```


### Slide 1
Based on these two graphs below, region 28 should be an area of focus for our company. With the second highest interest rate and the largest premium contributions, focusing our efforst on region 28 will increase earnings of our company.


```{r}
ggplot(region_summary_desc_10, aes(x = reorder(as.factor(Region_Code), Interest_Rate), y = Interest_Rate, fill = Interest_Rate)) +
  geom_bar(stat = "identity", color = "gray") +
  
  # Add text labels for Interest_Rate percentages
  geom_text(aes(label = paste0(round(Interest_Rate, 1), "%")), 
            hjust = -0.2, color = "black", size = 3.5) +
  
  # Apply continuous color scale from "Blue3"
  scale_fill_continuous_sequential(palette = "Mint") +
  
  # Remove y-axis ticks, labels, and grid lines
  scale_y_continuous(limits = c(0, 20), breaks = NULL) +
  
  # Flip coordinates for horizontal bars
  coord_flip() +
  
  # Labels for title and axes
  labs(
    title = "Key areas to maximize Conversion opportunities",
    subtitle = "Identifying top 10 regions with the highest interest rate",
    x = "Region Code",
    y = "",
    caption = "Source: Health Insurance Cross Sell Prediction- Kaggle") +
  theme_minimal() +
  theme(
    axis.text.x = element_blank(),  
    axis.ticks.x = element_blank(),  
    panel.grid.major.x = element_blank(),  
    panel.grid.minor.x = element_blank(),  
    panel.grid.major.y = element_blank(),  
    panel.grid.minor.y = element_blank(),
    legend.title = element_blank(),
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 13, face = "italic"),
    plot.caption = element_text(size = 10, hjust = 0, face="italic"),
    legend.position = "none",
  )
```

```{r}
# Order the data by Annual_premium in descending order
region_summary_desc_money <- region_summary %>%
  arrange(desc(total_annual_Premium))
# choose top 10
region_summary_desc_money_10 = region_summary_desc_money %>% 
  head(10)
```

```{r}
ggplot(region_summary_desc_money_10, aes(x = reorder(as.factor(Region_Code), total_annual_Premium), 
                                         y = total_annual_Premium, 
                                         fill = total_annual_Premium)) +
  geom_bar(stat = "identity", color = "gray") +
  scale_fill_continuous_sequential(palette = "Peach") +
  coord_flip()+
  labs(
    title = "High-Value Markets for Vehicle Insurance",
    subtitle = "Identifying top 10 regions with the largest premium contributions to prioritize marketing and sales efforts",
    x = "Region Code",
    y = "Total Annual Premium (Unit: 1 million dollars)",
    caption = "Source: Health Insurance Cross Sell Prediction-Kaggle") +
  theme_minimal() +
  theme(axis.text.x = element_text(vjust = 0.5, hjust = 1),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 12, face = "italic"),
        plot.caption = element_text(size = 10, hjust = 0, face="italic"),
        legend.position = "none")
```

```{r}
# Filter interested customer in region 28 
ds_28 = ds %>% 
  filter(Region_Code =="28", Response == "1")
```

```{r}
ggplot(ds_28, aes(x = Age)) +
  geom_density(fill = "lightblue", color = "darkblue", alpha = 0.7) +
  labs(
    title = "Age Distribution in Region 28: Key demographic Insights",
    subtitle = "Analyzing the age profile of interested customers to inform targeted marketing strategies",
    x = "Age",
    y = "Density",
    caption = "Source: Health Insurance Cross Sell Prediction-Kaggle"
  ) +
  theme_minimal()+
  theme(axis.text.x = element_text(vjust = 0.5, hjust = 1),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 12, face = "italic"),
        plot.caption = element_text(size = 10, hjust = 0, face="italic")
        )
```

In the two graphs below, we can see that the highest performing sales channel policies by average annual premium are by and large not commonly used in Region 28. Perhaps by shifting our sales channel policies we can maximize our profits.


```{r}
ds_28_premiums = ds_28 %>%
  group_by(Policy_Sales_Channel) %>%
  summarize(mean_premium = mean(Annual_Premium),
            med_premium = median(Annual_Premium),
            mean_age = mean(Age),
            sd_premium = sd(Annual_Premium),
            n = n()) %>% 
  filter(n > 10) %>% 
  arrange(desc(mean_premium))

ds_28_top_prem = ds_28_premiums[c(1:10),]

ggplot(ds_28_top_prem, aes(x = reorder(Policy_Sales_Channel, mean_premium), y = mean_premium, ymin = mean_premium- 1.96 * sd_premium / sqrt(n), ymax = mean_premium + 1.96 * sd_premium / sqrt(n))) + 
  geom_point(size = 2) + 
#  scale_fill_continuous_sequential(palette = "ag_GrnYl") + 
  theme_minimal() + 
  geom_errorbar(width = 0.5) + 
  labs(
    title = "Most Effective Sales Channels for Region 28",
    subtitle = "Top ten policy sales channels by mean annual premium in region 28",
    x = "Policy Sales Channel",
    y = "Mean Annual Premium",
    caption = "Source: Health Insurance Cross Sell Prediction-Kaggle"
  ) + 
  theme(axis.text.x = element_text(vjust = 0.5, hjust = 1),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 12, face = "italic"),
        plot.caption = element_text(size = 10, hjust = 0, face="italic"),
        legend.position = "none"
  ) + 
  coord_flip()
```

```{r}
ds_28_channel_count = ds_28 %>%
  group_by(Policy_Sales_Channel) %>%
  summarize(n = n()) %>% 
  filter(n > 10) %>% 
  arrange(desc(n))

ds_28_top_n = ds_28_channel_count[c(1:10),]

ggplot(ds_28_top_n, aes(x = reorder(Policy_Sales_Channel, n), y = n, fill = n)) + 
  geom_col() + 
  scale_fill_continuous_sequential(palette = "Emrld") + 
  theme_minimal() + 
  geom_text(aes(label = n), 
            hjust = -0.1, color = "black", size = 3.5) + 
  labs(
    title = "Most Used Sales Channels for Region 28",
    subtitle = "Top ten most commonly utilized policy sales channels in region 28",
    x = "Policy Sales Channel",
    y = "",
    caption = "Source: Health Insurance Cross Sell Prediction-Kaggle"
  ) + 
  theme(axis.text.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_blank(),
        plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 12, face = "italic"),
        plot.caption = element_text(size = 10, hjust = 0, face="italic"),
        legend.position = "none"
  ) + 
  coord_flip()
```


